Modelling the gas kinematics of an atypical Lyman alpha emitting compact dwarf galaxy

### 2017-06-15 paper/paper.tex
one less issue

\begin{figure*}
\begin{center}
  \includegraphics[width=0.6\textwidth]{vinf_cl.pdf}
  \includegraphics[width=0.6\textwidth]{P_cl.pdf}
  \includegraphics[width=0.6\textwidth]{sigma_cl.pdf}
\caption{Results from the multiphase  model.
  We only show results for the three parameters with a significant
  statistical difference between the models with the lowest $\chi^2$
  values and its prior distribution. 
  These three parameters are the clump radial velocity at infinity 
  $v_{\infty, \rm{cl}}$; the probability that  the \lya\ photons were
  emitted in the clumps, $P_{\rm cl}$; the clump velocity dispersion,
  $\sigma_{\rm cl}$.
  The left column corresponds to the parameter's integrated distributions for
  models with the lowest $\chi^2$ values (dotted line) compared against the
  parameter's prior integrated distributions (continuous line).
  The right column shows a scatter plot of $\chi^2$ (normalized by the
  degrees of freedom) and its corresponding physical parameters.
  This shows that the clump kinematic state is the key ingredient to
  reproduce \tol's \lya\ line morphology.
  \label{multiphaseresults}
}  
\end{center}
\end{figure*}

\begin{figure*}
\begin{center}
\includegraphics[width=0.8\textwidth]{emcee_results.pdf}
\caption{Results from the Markov Chain Monte Carlo computation for
    the rotation model. The dotted vertical lines in the outer histograms 
	represent the 16th, 50th and 84th percentiles. \label{emceeresults}} 
\end{center}
\end{figure*}

@@

The results are summarized in Figure \ref{multiphaseresults}.
Left panels show the difference between the integrated distributions
of the full sample (2500 input models) and the models with the lowest
$\chi^2$. 
The right panel shows the actual $\chi^2$ values and its corresponding
parameter value. 
Under these conditions we find $\sigma_{\rm cl}=$\sigmaclump,
$v_{\infty {\rm, cl}}=$\inftyclump\ and $P_{\rm cl}=$\probaclump.

Qualitatively, as \tol\ possesses a very wide spectrum which can be
achieved by subsequent scatterings off (relatively) fast moving clumps
while the multi-phase nature (i.e., the existence of low-density
channels) ensures the high flux at line center as observed.
In turn, a lower velocity dispersion would produce a thiner line than the
observed.
From the lower right panel in \ref{multiphaseresults} we find that it
is unlikely that the clump velocity dispersion is lower than
$50$\kms.

Why is it that the other parameters do not seem to matter? Probably
because $P_{cl}$ (the probability for a \lya\ to be emitted in a
clump) is high and most photons are produced at
large radii making the radiative transfer effects in the center less
important.  
We cannot discard that another region of parameter space with similar
velocity structure but empty interclump medium, relatively dense
clumps and at least a few clumps per sightline 
could also work \citep{Hansen06}.
This possibility does not change our conclusions about the
kinematic parameters, but it might be interesting to explore in the
future with a higher sampling of the parameter space once new
observations clarify the kinematic nature of \tol.

>>>>

\begin{figure*}
\begin{center}
  \includegraphics[width=0.6\textwidth]{vinf_cl.pdf}
  \includegraphics[width=0.6\textwidth]{P_cl.pdf}
  \includegraphics[width=0.6\textwidth]{sigma_cl.pdf}
\caption{Results from the multiphase  model.
  We only show results for the three parameters with a significant
  statistical difference between the models with the lowest $\chi^2$
  values and its prior distribution. 
  These three parameters are the clump radial velocity at infinity 
  $v_{\infty, \rm{cl}}$; the probability that  the \lya\ photons were
  emitted in the clumps, $P_{\rm cl}$; the clump velocity dispersion,
  $\sigma_{\rm cl}$.
  The left column corresponds to the parameter's integrated distributions for
  models with the lowest $\chi^2$ values (dotted line) compared against the
  parameter's prior integrated distributions (continuous line).
  The right column shows a scatter plot of $\chi^2$ (normalized by the
  degrees of freedom) and its corresponding physical parameters.
  The clump kinematic state is the key ingredient to
  reproduce \tol's \lya\ line morphology.
  \label{multiphaseresults}
}  
\end{center}
\end{figure*}

\begin{figure*}
\begin{center}
\includegraphics[width=0.8\textwidth]{emcee_results.pdf}
\caption{Results from the Markov Chain Monte Carlo computation for
    the rotation model. 
    The gray scale indicates the point density in parameter space. 
    The dotted vertical lines in the histograms in the diagonal panels
    represent the 16th, 50th and 84th percentiles. 
    All parameters in the rotation model can be succesfuly constrained by \tol's
    \lya\ line morphology to the values written in the top region of
    the diagonal panels.
    \label{emceeresults}} 
\end{center}
\end{figure*}

@@

The results are summarized in Figure \ref{multiphaseresults}.
Left panels show the difference between the integrated distributions
of the full sample (2500 input models) and the models with the lowest
$\chi^2$. 
The right panel shows the actual $\chi^2$ values (normalized by the
degrees of freedom) and its corresponding parameter value. 
Under these conditions we find $\sigma_{\rm cl}=$\sigmaclump,
$v_{\infty {\rm, cl}}=$\inftyclump\ and $P_{\rm cl}=$\probaclump.

Qualitatively this can be understood as follows. The broad \lya\ line
is the result of subsequent \lya\ photon scatterings due to
(relatively) fast moving clumps while the multi-phase nature (i.e., the existence of low-density
inter-clump regions where \lya\ photons can freely prograpagate)
ensures the high flux at line center as observed.  
In turn, a lower velocity dispersion would produce a thiner line than
it is observed.
From the lower right panel in Figure \ref{multiphaseresults} we find that it
is unlikely that the clump velocity dispersion is lower than
$50$\kms.

Why is it that the other parameters do not seem to matter? Probably
because $P_{cl}$ (the probability for a \lya\ to be emitted in a
clump) is high and most photons are produced at
large radii making the radiative transfer effects in the center less
important.  
We cannot discard that another region of parameter space with similar
velocity structure but an empty inter-clump medium, relatively dense
clumps and at least a few clumps per sightline 
could also work \citep{Hansen06}.
This possibility does not change our conclusions about the
kinematic parameters, but it might be interesting to explore in the
future with a higher sampling of the parameter space once new
observations clarify the kinematic nature of \tol.
